\documentclass [11pt, twoside] {uwthesis}[2012/06/19]

\usepackage{amsmath, graphicx, natbib, listings, lscape, longtable,hyperref}
\def\bibpreamble{\protect\addcontentsline{toc}{chapter}{Bibliography}}

\setcounter{tocdepth}{1}  % Print the chapter and sections to the toc

\usepackage{alltt}  %
\newenvironment{demo}
  {\begin{alltt}\leftskip3em
     \def\\{\ttfamily\char`\\}%
     \def\{{\ttfamily\char`\{}%
     \def\}{\ttfamily\char`\}}}
  {\end{alltt}}

% metafont font.  If logo not available, use the second form
%
% \font\mffont=logosl10 scaled\magstep1
\let\mffont=\sf
% --- end-of-sample-stuff ---

\begin{document}

% ==========   Preliminary pages
%
% ( revised 2012 for electronic submission )
%

\prelimpages

%
% ----- copyright and title pages
%

\Title{Source, propagation, and effects of lightning in the Earth-ionosphere system}
\Author{Michael L. Hutchins}
\Year{2014}
\Program{UW Department of Earth and Space Sciences}

\Chair{Robert H. Holzworth}{Professor}{Department of Earth and Space Sciences}
\Signature{Michael P. McCarthy}
\Signature{Abram R. Jacobson}
\Signature{John M. Wallace}
\Signature{John D. Sahr}

\copyrightpage

\titlepage

%
% ----- abstract
%

\setcounter{page}{-1}
\abstract{

The capabilities of the World Wide Lightning Location Network (WWLLN) are expanded to enable research of the source, propagation, and effects of lightning in the Earth-ionosphere system.
The main expansion of the network is the measurement of the very low frequency radiated energy from lightning; the radiated stroke energy is directly proportional to the canonical peak current measurements of other ground based networks.
Stroke energy is used to develop a model of the network relative detection efficiency; this internal model rates the coverage capabilities of the network compared to the networks best coverage.
The last dataset developed and discussed is the clustering of the lightning locations into both flashes and the active lightning regions of thunderstorms.
These three capabilities of the network allow tracing the effects of lightning and thunderstorms from their source to the global electric circuit and to the magnetosphere.

The source of lightning is investigated in two regimes: within thunderstorms and between thunderstorms.
Within thunderstorms the time between flashes is found to be proportional to the resulting flash energy for differing thunderstorms, regions, and seasons.
Between thunderstorms the lightning energy is shown to differ between land and ocean, with oceanic thunderstorms producing stronger and fewer strokes.
The propagation of the radiated energy is measured using the lightning as a probe of attenuation along the different propagation paths.
Attenuation is seen to have an asymmetry with magnetic azimuth: eastward moving waves are attenuated less than westward moving waves.
The attenuation asymmetry is complimentary to the observed asymmetry in whistler and radio energy emitted through the ionosphere into the magnetosphere.
Thunderstorm clusters are used to estimate the total upward current contribution of thunderstorms to the global electric circuit.
It is shown that WWLLN can provide one of the first continuous global measurements of this current to the global electric circuit.

}

%
% ----- contents & etc.
%

\tableofcontents
\listoffigures

\listoftables  % I have no tables

%
% ----- glossary
%

%\chapter*{Glossary}      % starred form omits the `chapter x'
%\addcontentsline{toc}{chapter}{Glossary}
%\thispagestyle{plain}
%
%\begin{glossary}
%\item[WWLLN] a network.

%\end{glossary}

%
% ----- acknowledgments
%

\acknowledgments{
I would like to thank everyone in the University of Washington Earth and Space Sciences department: colleagues, classmates, mentors, advisors, and friends.
I want to thank my advisor Robert Holzworth for providing the environment to succeed and develop from the start to the end of my degree.
Michael McCarthy, Abram Jacobson, and John Wallace have greatly helped throughout with discussions of ideas, methods, and research.

I would like to thank Ariah Kidder for providing guidance, mentorship, and much needed distractions.
From across campus I want to thank James Pfeiffer for the discussions of math and programming.
Finally I want to thank my wife Leah Ganis for the constant support and encouragement for finishing in a timely manner.
}

%
% ----- dedication
%

\dedication{\begin{center}To Leah\end{center}}

%
% end of the preliminary pages

%
% ==========      Text pages
%

\textpages

% ========== Chapter Introduction

\chapter{Introduction}
\label{thesis:chapter:introduction}

\include{Introduction/introduction}

% ========== Chapter Stroke Energy

\chapter{Stroke Energy}
\label{thesis:chapter:energy}

\include{Energy/energy}

% ========== Chapter WWLLN Detection Efficiency

\chapter{WWLLN Detection Efficiency}
\label{thesis:chapter:efficiency}

\include{Efficiency/efficiency}

% ========== Chapter ENTLN-LIS Detection Efficiency

\chapter{ENTLN-LIS Detection Efficiency}
\label{thesis:chapter:entln-lis}

\include{ENTLN_LIS/entln_lis}

% ========== Chapter Land-Sea Contrast

\chapter{Land-Sea Contrast}
\label{thesis:chapter:landsea}

\include{LandSea/landsea}

% ========== Chapter VLF Propagation

\chapter{VLF Propagation}
\label{thesis:chapter:prop}

\include{Azimuth/azimuth}


% ========== Chapter Global Electric Circuit

\chapter{Global Electric Circuit}
\label{thesis:chapter:gec}

\include{GEC/gec}

% ========== Thunderstorms

\chapter{Thunderstorms and Flashes}
\label{thesis:chapter:thunderstorm}

\include{Thunderstorm/thunderstorm}

% ========== Conclusion and Future Work

\chapter{Conclusion and Future Work}
\label{thesis:chapter:conclusion}

\include{Conclusion/conclusion}


%
% ==========   Bibliography
%

%\nocite{*}   % include everything in the uwthesis.bib file
\bibliography{/users/michael/documents/ess/research/library}
\bibliographystyle{/users/michael/documents/ess/research/agu}


%
% ==========   Appendices
%

\appendix
\raggedbottom\sloppy

% ========== Appendix Code

\chapter{Code Repositories}
\label{thesis:appendix:code}

\include{Appendix/code}

% ========== Appendix Bootstrap

\chapter{Energy Processing}
\label{thesis:appendix:energy}

\include{Appendix/bootstrap}

% ========== Appendix Service Unit

\chapter{WWLLN Service Unit v4}
\label{thesis:appendix:su}

\include{Appendix/su}

% ========== Appendix Gumstix

\chapter{Gumstix}
\label{thesis:appendix:gumstix}

\include{Appendix/gumstix}

% ========== Appendix Gumstix

\chapter{Website}
\label{thesis:appendix:website}

\include{Appendix/website}

\vita{Michael Hutchins was born in Santa Rosa, California in 1987.
He had an uncomplicated childhood set amidst the vineyards of the Sonoma wine country.
Without any inherent struggles or tragedies in his life to fuel an artistic career, he left Northern California to attend the University of California Santa Barbara for a BS in Physics.
He spent his third year at UCSB abroad studying Astrophysics at the University of Edinburgh, Scotland where a chance assumption directed him to graduate school.
In 2009 he eschewed a move away from the West Coast to attain his PhD in Earth and Space Sciences studying lightning at the University of Washington, Seattle.
}

\end{document}
