My work in this dissertation started with the WWLLN producing only lightning stroke locations and uncalibrated RMS energy values of the detected strokes.
To enable new and extended analysis with the dataset I developed techniques to measure the energy per stroke, model the relative detection efficiency of the network, and cluster lightning into flashes and thunderstorms.
To prove and validate the new techniques they were applied to problems and questions that have only been addressed with limited extent or duration; the new techniques allowed for broader, longer, and more detailed analysis.

The new analysis were: an examination of the difference between continental and oceanic thunderstorm energies, the dependence of VLF propagation on magnetic azimuth, a model of the thunderstorm contribution to the global electric circuit, and an analysis of observed thunderstorm and flash properties.
These analysis were made using WWLLN by itself or in conjunction with other lightning detection systems.

Most of the research completed here naturally leads to future projects and research avenues that can be explored in the context of this work.
Several of the possibilities for research with WWLLN are: network characterization, thunderstorms, the global electric circuit, and other lightning processes are discussed in this chapter.

\section{WWLLN Characterization}

The relative detection efficiency model developed in Chapter~\ref{thesis:chapter:efficiency} provides one view of the WWLLN network performance but it relies on several assumptions.
Either the model can be advanced to not rely on these assumptions or those assumptions themselves can be directly monitored.
The main assumption is that the distribution of lightning energy is the same everywhere; this was seen not to hold in Chapter~\ref{thesis:chapter:landsea} between land and oceanic thunderstorms.
The model can take into account the varying energy distributions, or the expected variance, through the variability of the observed regional energy distributions over time.

A promising method for examining the energy detection efficiency is to check how the measured energy values change when the station configuration changes.
For example, processing the energy data after artificially removing a few stations to quantify how the energy distributions change.
Compare the two energy distributions to the change in detection efficiency relative to a reference network (e.g. ENTLN or LIS) to better parameterize the model.

Similarly, the accuracy of the energy measurements themselves can be improved by adapting the energy per stroke processing to include multiple well calibrated WWLLN stations.
In the processing described in this work the entire network calibration is bootstrapped from one station; the addition of a second well calibrated station can improve the energy measurements and help quantify the regional variation in energy uncertainty.
This can address the uncertainty that is introduced in the station calibrations for stations far from the first station.

Finally other network characterizations can be developed based on the clustering results.
The number of thunderstorms, the average number of strokes per thunderstorm, average flash multiplicity, or time between flashes within a single thunderstorm can be routinely monitored for network health.

\section{Thunderstorms}

\subsection{Cluster Validation}

The thunderstorm clustering discussed in Chapter~\ref{thesis:chapter:gec} and~\ref{thesis:chapter:thunderstorm} can benefit from additional validation.
Two potential methods for validation are large scale comparisons to TRMM precipitation rates and case studies against regional weather radars.
The TRMM comparison would require grouping of the precipitation data to compare to the estimated thunderstorm extents.
Weather radar comparisons would provide detailed ground truth of the thunderstorm cluster areas and durations; further, weather radar would allow for a measure of thunderstorm tracking accuracy.

Aside from comparisons to other systems the properties measured by the thunderstorm clustering can be tracked over spatial and temporal scales.
For example: the average thunderstorm duration interannual variability in a given region or the overall network observed thunderstorm area.
This can explore the changes in the clustering values and accuracy as the stroke rate detected by WWLLN changes with time.

\subsection{Parameterization}

Thunderstorm parameterizations are functional relationships between different properties of thunderstorms.
Using lightning detection networks allows for the development of these relationships that infer thunderstorm properties based on the observed lightning flash rates; of particular benefit for regions with low availability of direct observations (e.g. radar, satellite).
\citet{Zipser1994} examined the relation between the flash rate in a thunderstorm with the updraft velocities, which in turn are controlled by the differential surface heating below the thunderstorm.
Parameterization of flash rate based on other observations has led to simple models of global lightning behaviour; \citet{Price1992} used cloud height parameterization for flash rate.
These empirical parameterizations can help in the development and validation of models (e.g. \citet{Baker1999}) of thunderstorm electrification and enable or expand prediction of the global electric circuit, NO$_\text{x}$ production, and weather forecasting.
Investigating the parameterization of lightning behavior in relation to the properties of a thunderstorm on a large scale can create better and more robust parameterizations.
The WWLLN thunderstorm clustering can be compared to other networks and systems in order to develop and validate new parameterizations.

\subsection{Thunderstorm Properties}

The WWLLN thunderstorm clustering can be used to investigate global and regional thunderstorm properties and their distributions.
Thunderstorm area and duration are briefly discussed in Chapter~\ref{thesis:chapter:thunderstorm}, but can be explored in more depth and in more regions.
These two properties can be measured over different spatial and temporal scales.
For example the distribution of winter thunderstorms over the Sea of Japan \citep{Ishii2010}, or the South American ``green ocean'' phenoma \citep{Williams2002}.

Alternatively more complex measures of thunderstorms can be developed: the average stroke count per thunderstorm, the peak flash rate, or the electrical activity.
The electrical activity can be measured as the total flash energy per unit area per unit time for the thunderstorm: the sum of measured flash energies within the thunderstorm.
This measure, and others, may be highly dependent on the network performance or may not be absolutely calibrated, however they can still allow for relative comparisons between thunderstorms in a limited temporal or spatial scope (e.g. North America in July 2013).

The thunderstorm dataset can also be advanced by classifying thunderstorms into different thunderstorm types.
While this may only work for small case studies it may be possible to use more advanced machine learning classifiers to automatically assign cloud types to thunderstorm clusters.

\section{Global Electric circuit}

The global electric circuit model presented in Chapter~\ref{thesis:chapter:gec} provides an estimate of the thunderstorm contribution to the circuit based on the WWLLN thunderstorm clusters.
It is shown that the model is able to reproduce the expected Carnegie curve over long time scales and has the capability to provide current estimates on shorter time scales.
The model can be improved for a more accurate measure of the current contribution, but without any validation it cannot be reliably used.

To improve the model there are several underlying assumptions that can be factored in.
The main one is that all thunderstorms produce the same upward current to the ionosphere regardless of their size or activity.
The estimates used in the model from \citet{Mach2010} can be scaled by either the thunderstorm cluster activity or the estimated cluster size.
Since the development of the model the thunderstorm cluster area was validated against ENTLN in Chapter~\ref{thesis:chapter:thunderstorm}, giving confidence to the area measurements.
The second assumption is that WWLLN detects 99\% of thunderstorms, an assumption explored in Chapter~\ref{thesis:chapter:thunderstorm}.
The third assumption is that all thunderstorm currents are the same everywhere.
This assumption is harder to address as it relies on direct measurements of the current made in different regions.

Regardless of the model improvements made, the model needs to be compared against a ground truth measurement.
Further, comparison to a ground truth will allow for tuning of the model to better fit the observed measurements; or if adjustments cannot be made then other components of the global electric circuit need to be included in the model.
For the ground truth a balloon campaign needs to be conducted to measure the fair weather return current over the span of one to several weeks.
With a reliable and clean measurements of the return current the model can be validated on a very short time scale instead of relying on long term averages.

\section{Other Lightning Processes}

WWLLN is able to measure and detect more than just the main discharge of a lightning stroke.
The network is able to directly detect terrestrial gamma-ray flashes (TGF) and their related strokes, it is also able to detect whistler waves at the individual stations.
For TGFs WWLLN has been used to geolocate the TGF itself and the originating thunderstorm \citep{Connaughton2010, Connaughton2013}.
WWLLN can be used to create an estimate of the global TGF production rate by comparing the detected TGFs with the lightning within view of one of the TGF satellites (e.g. FERMI or RHESSI).
With whistler waves an automated whistler detector running at the remote WWLLN stations could enable the creation of a large database of whistler waves.
Such a database could provide the means for investigations of the ionosphere and magnetosphere, especially if the detector is able to run on multiple WWLLN stations.
The advantage of a WWLLN based system compared to existing systems is the potential to use the existing distribution of stations and to develop a new system that can run on unspecialized hardware.


